---
title: 'Macroeconomics'
subtitle: 'Assignment 4'
author: "Your name"
date: '`r format(Sys.time(), "%d %b, %Y")`'
output: pdf_document
fontsize: 12pt
classoption: a4paper
urlcolor: blue
---

## Question 1: SVAR Modelling of Supply and Demand Disturbnces
We replicated the results of Blanchard (1989), A Traditional Interpretation of Macroeconomic Fluctuations, AER, 79(5) during lectures in the computer lab. Specifically, we estimated the IRFs (pp1159-60) for a sample covering 1965 to 1986. 

Your assignment is to run Blanchard's model for data from 1987 to 2018. 

The code to download the data is in the structural VAR lecture slides 8 and 9. Calculate IRFs and FEVDs. 

Are your results broadly consistent with those in Blanchard's article? Discuss the macroeconomic implications of your IRF and FEVD results.


<!-- Answer here -->

```{r}

```

## Question 2: 

Summarise the results of Miyao (2002) and Uhlig (2005) regading the effects of monetary policy (in your own words). Write one to two pages.


<!-- Answer here -->




## Question 3:

In the final lecture we examine Gali (1999). Run Gali's model on data for 1948-2018 and 1996-2018.Use the data we download in class. Are your results similar to Gali's original results? Comment and interpret your results.

<!-- Answer here -->

```{r}

```




